\documentclass[12pt,a4]{article}



\input{preamble}



\setcounter{section}{2}


\begin{itemize}
 \item Homework assignment published on Tuesday, 2018-03-13
 \item Submit questions and first solutions by Sunday, 2018-03-18, 12:00 by email to dominik.scheder@gmail.com  and the TAs.
 \item You will receive feedback by Wednesday, 2018-03-21
 \item Revise your solution and submit your final solution by Sunday, 2018-03-25 by  email to dominik.scheder@gmail.com and the TAs.
\end{itemize}



\section{Basic Counting}

A function $[m] \rightarrow [n]$ is {\em monotone} if $f(1) \leq f(2) \leq \dots \leq f(m)$.
It is  {\em strictly monotone} if $f(1) < f(2) < \dots < f(m)$.

\begin{exercise}
   Find and justify a closed formula for the number of strictly
   monotone functions from $[m]$ to $[n]$.
\end{exercise}
\textbf{Solution.}
    We choose $m$ elements in $[n]$, and match each one with the element in $[n]$ with the same order. Note that if $n < m$, there is no feasible matching like that, and the solution is $0$.
$$
    N_{m,n}=\binom{n}{m}
$$

\begin{exercise}
   Find and justify a closed formula for the number of monotone functions from $[m]$ to $[n]$.
\end{exercise}
\textbf{Solution.}
    We choose $1$ to $m$ elements in $[n]$, and then we need to allocate elements in $[m]$ to them. If we choose $i$ elements in $[n]$, $[m]$ needs to be divided into $i$ parts. Note that elements in each part is continuous in order, so we can insert $i-1$ plates into intervals of $[m]$, where there are $m-1$ intervals. Then we can use the formula $\binom{n}{m}=\binom{n}{n-m}$. At last we can use a combinatorial interpretation to get the final formula for the number of monotone functions from $[m]$ to $[n]$.
$$
    N_{m,n}=\sum^m_{i=0}(\binom{n}{i}\times\binom{m-1}{i-1})=\sum^m_{i=1}(\binom{n}{i}\times\binom{m-1}{m-i})=\binom{m+n-1}{m}
$$

\textbf{Remark.} By ``closed'' I mean something using expressions like $\times$, $+$,
${n \choose k}$, $n!$, but not $\sum$ or $\prod$.
For example, ${n \choose k^2}$ is a closed formula but
$\sum_{k=0}^n {n \choose k}$ is not.


\begin{exercise}
  Prove that $\sum_{k=0}^n {n \choose k}^2 = {2n \choose n}$ for every $n \geq 0$ by finding a combinatorial interpretation.
\end{exercise}
\textbf{Solution.}
    Obviously $\sum_{k=0}^n {n \choose k}^2 = \sum_{k=0}^n {n \choose k}\times{n \choose {n-k}}$. Assume there are two sets each of which has $n$ elements, and we need to choose $n$ elements from them. One way is to choose $k$ ($0\leq k\leq n$) elements from one set and then choose $n-k$ elements from the other, which is $\sum_{k=0}^n {n \choose k}^2$. Another way is to see them as a whole which has $2n$ elements, and then we choose $n$ elements from it, which is ${2n \choose n}$.
\begin{exercise}[From the textbook]
   Find a closed formula for $\sum_{k=m}^n {k \choose m}{n \choose k}$ and prove it combinatorially, i.e., by giving an
   interpretation.
\end{exercise}

\begin{exercise}
   Let $B_n$ be the number of partitions of the set $[n]$ (this is the same as the number
   of equivalence relations on $[n]$). This is called the Bell number, thus we
   denote it $B_n$.
   Prove that the following recursive formula
   for $B_n$ is correct:
   \begin{align*}
     B_0 & = 1 \\
     B_{n+1} & = \sum_{k=0}^n {n \choose k} B_k  \ .
   \end{align*}
\end{exercise}

\begin{exercise}
  Let $P_n$ be the number of ways to write the natural number $n$ as a sum $
  a_1 + a_2 + \cdots + a_k$ such that
  $1 \leq a_1 \leq a_2 \leq \dots \leq a_k$. For example, $3$ can be written
  as $3$, $2 + 1$, and $1 + 1 + 1$, so $P_3 = 3$.
   Find a recursive formula for $P_n$.\\

   \textbf{Remark.} The formula might not be as simple as the above for $B_n$. Be creative!
   Start by writing a simple recursive program that computes $P_n$.
\end{exercise}



\end{document}

